The Shot Predictor

### 2022-10-16 Papers/PaperForReview.tex
Add General Overview of Methdology

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit your finished paper.
We MUST have this form before your paper can be published in the proceedings.

Please direct any questions to the production editor in charge of these proceedings at the IEEE Computer Society Press:
\url{https://www.computer.org/about/contact}.

>>>>

%------------------------------------------------------------------------
\section{Methodology}
\subsection{General Overview}
We will have a camera taking in video input of a player shooting the basketball, potentially from two different angles.
One angle would be a side view of the shooter that can capture the relative positions of the shooter and the hoop, and the other
would be a head-on view of the of the shooter to capture the full pose estimation of the shooter.

In the background, we will have our pose estimation algorithm running to capture the pose estimation of the shooter which will be used
to make our predictions. Additionally, we will potentially be retrieving other data to create our feature vector, including the angle relationship
between the shooter and the hoop, and the speed of the shot. We will be attempting to capture the pose estimation at multiple stages of the
shot, as each stage can have a significant impact on the outcome of the shot. We will then take this feature vector and put it through a classification model.
We will perform binary classification and predict whether a shot will go in or not.
